---
title: "Slides"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r share-again, echo=FALSE}
xaringanExtra::use_share_again()
```

```{r embed-xaringan1, echo=FALSE, fig.cap="[Slides](slides/01-introduction/index.html)"}
xaringanExtra::embed_xaringan(url = "slides/01-introduction/index.html", ratio = "16:9")
```

<aside>
First set of slides. These slides introduces the instructor, the material being taught and general guidelines. This is being seperated into their own slides for ease of access.  
[Full screen link](slides/01-introduction/index.html)
</aside>

```{r embed-xaringan2, echo=FALSE, fig.cap="[Slides](slides/02-text-mining/index.html)"}
xaringanExtra::embed_xaringan(url = "slides/02-text-mining/index.html", ratio = "16:9")
```

<aside>
Second set of slides. These slides will introduce the data set we will be using and to do some rudimentary text mining to get us familiar with the data.  
[Full screen link](slides/02-text-mining/index.html)
</aside>

```{r embed-xaringan3, echo=FALSE, fig.cap="[Slides](slides/03-modeling/index.html)"}
xaringanExtra::embed_xaringan(url = "slides/03-modeling/index.html", ratio = "16:9")
```

<aside>
Third and final set of slides. These slides will showcase how we can use [tidymodels](https://www.tidymodels.org/) and [textrecipes](https://textrecipes.tidymodels.org/) to build predictive models that use text as features.  
[full screen link](slides/03-modeling/index.html)
</aside>
